Emergent dual scaling of riverine biodiversity

### 2021-03-25 coverletter.Rmd
Update coverletter.Rmd

Despite the inherent complexity of nature, some ecological patterns follow simple mathematical rules with far-reaching implications for biodiversity conservation. Much attention has been paid to the ubiquitous power-law scaling between species richness and area, in which species richness increases with area in a decelerating way. In spatially complex ecosystems, however, there may be an overlooked scaling law of biodiversity because 'scale-invariant' complexity of fractal ecosystem structure drives ecological dynamics in space. Branching river networks are an outstanding example of such complex ecosystems, where geometric ecosystem structure (e.g., branching patterns) remains constant across a wide range of spatial scales.

>>>>

Despite the inherent complexity of nature, some ecological patterns follow surprisingly simple rules with far-reaching implications for biodiversity conservation. Much attention has been paid to the ubiquitous power-law scaling between species richness and area, in which species richness increases with area in a decelerating way. In spatially complex ecosystems, however, there may be an overlooked scaling law of biodiversity because 'scale-invariant' complexity of fractal ecosystem structure drives ecological dynamics in space. Branching river networks are an outstanding example of such complex ecosystems, where geometric ecosystem structure (e.g., branching patterns) remains constant across a wide range of spatial scales.
